Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-16 doc/manuscript/ESSDmanuscript.Rmd
trying to make table work
updates related to land management categories

**The International Panel on Climate Change (IPCC) provides guidance for national greenhouse gas inventories [(REFS for older guidelines), @ipcc_2019_2019].**
These include guidance for accounting for forest land [@ipcc_agriculture_2006; @ipcc_2019_2019a].
This guidance has improved as more of the relevant underlying data has become available [@requenasuarez_estimating_2019], but there remains room for continuous improvement as the science advances.
For example, @cook-patton_mapping_2020 *(summarize IPCC comparison results)*. 
*Moreover, it is useful for those compiling national greenhouse gas inventories to have access to locally-specific information, when available.*
To improve the data accessible for C accounting, the IPCC created the Emission Factor Database (EFDB; https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a recognized library of emission factors and other parameters that can be used for estimating greenhouse gas emissions and removals.

@@

For quantifying forest role in global C cycle, we ultimately care about:
(1) C stocks --stores of C that would be released to the atmosphere upon and use change
(2) C increments -- changes in those C stocks.

@@

@@

>>>>

**The International Panel on Climate Change (IPCC) provides guidance for national greenhouse gas (GHG) inventories for reporting to the United Nations Framework Convention on Climate Change [UNFCCC, (REFS for older guidelines), @ipcc_2019_2019].**
Under this guidance, GHG inventories are to include all managed land, including most of the world's forest land [@ogle_delineating_2018].
The IPCC inventory guidelines include specific instructions for accounting for forest land ... [@ipcc_agriculture_2006; @ipcc_2019_2019a].
This guidance has improved as more of the relevant underlying data has become available [@requenasuarez_estimating_2019], but there remains room for continuous improvement as the science advances.
For example, @cook-patton_mapping_2020 *(summarize IPCC comparison results)*. 
*Moreover, it is useful for those compiling national greenhouse gas inventories to have access to locally-specific information, when available.*
To improve the data accessible for C accounting, the IPCC created the Emission Factor Database (EFDB; https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a recognized library of emission factors and other parameters that can be used for estimating greenhouse gas emissions and removals.

@@

For quantifying forest role in global C cycle, we ultimately care about:
(1) C stocks -- stores of C that would be vulnerable to release to the atmosphere upon land use change
(2) C increments -- changes in those C stocks.

@@

```{r eval = FALSE, echo=FALSE, warning=FALSE}
#another failed attempt at the table
library(flextable)
C_pools_table <- read.csv("figures_tables/C_pools.csv")
ft <- flextable(C_pools_table)
ft

```

@@

Documented at https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/defining_land_subcategory.md, https://github.com/forc-db/IPCC-EFDB-integration/blob/main/doc/ForC-EFDB_mapping/IPCC_LandUse_mapping.csv, and in [issue #8](https://github.com/forc-db/IPCC_database_integration/issues/8).

The UNFCCC requires GHG reporting for all managed lands in a country, where management is defined as "human interventions and practices have been applied to perform production, ecological or social functions" [*IPCC 2006 full report REF*]. 
This definition is applied differently across countries, and is not clearly defined by the majority of governments [@ogle_delineating_2018]. 
Given this, and because the IPCC definition of management does not necessarily match that which would be reported in scientific publications and hence in ForC, we do not transfer any classification of land management status from ForC to the EFDB, but do provide auxiliary info that may be useful in making this determination (e.g., geographical location).

### 2021-06-16 doc/manuscript/ESSDmanuscript.tex
updates related to land management categories

\textbf{The International Panel on Climate Change (IPCC) provides
guidance for national greenhouse gas inventories \citep[(REFS for older
guidelines),][]{ipcc_2019_2019}.} These include guidance for accounting
for forest land \citep{ipcc_agriculture_2006, ipcc_2019_2019a}. This
guidance has improved as more of the relevant underlying data has become
available \citep{requenasuarez_estimating_2019}, but there remains room
for continuous improvement as the science advances. For example,
\citet{cook-patton_mapping_2020} \emph{(summarize IPCC comparison
results)}. \emph{Moreover, it is useful for those compiling national
greenhouse gas inventories to have access to locally-specific
information, when available.} To improve the data accessible for C
accounting, the IPCC created the Emission Factor Database (EFDB;
https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a
recognized library of emission factors and other parameters that can be
used for estimating greenhouse gas emissions and removals.

@@

Land classification under UNFCCC (e.g.,
https://cbmjournal.biomedcentral.com/articles/10.1186/s13021-018-0095-3)
is (i) defined differently across countries and (ii) probably not
defined the same way as it might be defined in publications included in
ForC. Therefore, we do not transfer any classification of land as
managed/unmanaged, but do provide any auxiliary info that may be useful
in making this determination.

>>>>

\textbf{The International Panel on Climate Change (IPCC) provides
guidance for national greenhouse gas (GHG) inventories for reporting to
the United Nations Framework Convention on Climate Change \citep[UNFCCC,
(REFS for older guidelines),][]{ipcc_2019_2019}.} Under this guidance,
GHG inventories are to include all managed land, including most of the
world's forest land \citep{ogle_delineating_2018}. The IPCC inventory
guidelines include specific instructions for accounting for forest land
\ldots{} \citep{ipcc_agriculture_2006, ipcc_2019_2019a}. This guidance
has improved as more of the relevant underlying data has become
available \citep{requenasuarez_estimating_2019}, but there remains room
for continuous improvement as the science advances. For example,
\citet{cook-patton_mapping_2020} \emph{(summarize IPCC comparison
results)}. \emph{Moreover, it is useful for those compiling national
greenhouse gas inventories to have access to locally-specific
information, when available.} To improve the data accessible for C
accounting, the IPCC created the Emission Factor Database (EFDB;
https://www.ipcc-nggip.iges.or.jp/EFDB/main.php), which is intended as a
recognized library of emission factors and other parameters that can be
used for estimating greenhouse gas emissions and removals.

@@

The UNFCCC requires GHG reporting for all managed lands in a country,
where management is defined as ``human interventions and practices have
been applied to perform production, ecological or social functions''
{[}\emph{IPCC 2006 full report REF}{]}. This definition is applied
differently across countries, and is not clearly defined by the majority
of governments \citep{ogle_delineating_2018}. Given this, and because
the IPCC definition of management does not necessarily match that which
would be reported in scientific publications and hence in ForC, we do
not transfer any classification of land management status from ForC to
the EFDB, but do provide auxiliary info that may be useful in making
this determination (e.g., geographical location).
